---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- [![Build Status](https://travis-ci.org/hrbrmstr/blocklist.svg)](https://travis-ci.org/hrbrmstr/blocklist) 
![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/blocklist)](http://cran.r-project.org/web/packages/blocklist) 
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/blocklist) -->

`blocklist` : Tools to Work with the <blocklist.de> 'API'

The following functions are implemented:
- `get_last_added_ips` : Query <blocklist.de> API for IPs blocked in since a period in time, optionally filtering by service

### News

- Version 0.1.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/blocklist")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(blocklist)

# current verison
packageVersion("blocklist")

# defaults
get_last_added_ips()

# last half hour
get_last_added_ips(1800)

# since 10PM today
#get_last_added_ips("22:00")

# for ssh blocks in the last half hour
get_last_added_ips(1800, "ssh")
```

### Test Results

```{r}
library(blocklist)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
